Untitled

### 2019-08-23 IPCO_NS.Rmd
updated

@@

library(made4)

@@

k.coa<- ord(inferred_MetaCyc, type="coa")
summary(k.coa$ord)

@@

>>>>

setwd("/Users/Nik/globalmicrobiome")

@@

# Create mnd variable
# grabs the nationality from phyloseq
con.class <- get_variable(pseq, "nationality" )

# check you've installed this library
library(forcats)

# this collapses the two varialbes into a new variable AB in this case. The command for multiple changes is fct_collapse(x, AB = c("A","B"), DE = c("D","E"))
mnd.class <- fct_collapse(con.class, LOW = c("Scandinavia","EasternEurope") , MEDIUM = c("SouthEurope","CentralEurope", "UKIE"), HIGH = c("US") )

# reorder
mnd.class <- factor(mnd.class, levels = (c("LOW", "MEDIUM", "HIGH")))

library(made4)
library(ade4)

@@

```{r , include=FALSE}

#p <- overview(inferred_MetaCyc,classvec=mnd.class, labels=c("red", "blue", "yellow"))

#Correspondence Analysis
#The function ord simplifies the running of ordination methods such as principal component, correspondence or non-symmetric correspondence analysis. It provides a wrapper
#which can call each of these methods in ade4. To run a correspondence analysis [6] on
#this dataset.

k.coa<- ord(inferred_MetaCyc, type="coa")
summary(k.coa$ord)
p <- plot(k.coa)

p <- plot(k.coa, classvec=mnd.class, arraycol=c("red", "blue", "yellow" ), genecol="grey3")

```{r , include=FALSE}
plotarrays(k.coa, arraylabels=mnd.class)

@@

k.coa2<-ord(inferred_MetaCyc, classvec=mnd.class)
p <- plot(k.coa2)

#Classification and Class Prediction using Between Group
#Analysis
#Between Group Analysis (BGA) is a supervised classification method [3]. The basis
#of BGA is to ordinate the groups rather than the individual samples. In tests on two
#microarray gene expression datasets, BGA performed comparably to supervised classification methods, including support vector machines and artifical neural networks [2].
#To train a dataset, use bga, the projection of test data can be assessed using suppl.
#One leave out cross validation can be perfo

k.bga<-bga(inferred_MetaCyc, type="coa", classvec=mnd.class)
between.graph(k.bga, ax=1) # Show the separation on the first axes(ax

#Meta-analysis of microarray gene expression
#Coinertia analysis cia [4] has been successfully applied to the cross-platform comparison
#(meta-analysis) of microarray gene expression datasets [8]. CIA is a multivariate method
#that identifies trends or co-relationships in multiple datasets which contain the same
#samples. That is either the rows or the columns of a matrix must be ”matchable”. CIA
#can be applied to datasets where the number of variables (genes) far exceeds the number
#of samples (arrays) such is the case with microarray analyses. cia calls coinertia in
#the ade4 package. See the CIA vignette for more details on this method.

#By default the variables (genes) are labelled with the rownames of the matrix. Typically these are spot IDs or Affymetrix accession numbers which are not very easy to
#interpret. But these can be easily labeled by your own labels. For example its often
#useful to labels using HUGO gene symbols. We find the Bioconductor annotate and
#annaffy annotation packages are very useful for this. Alternatively we also use biomaRt
#or Resourcerer or the Stanford Source database.
#In this example we provide annotation from the Source database in khan$annotation.
#The gene symbol are in the column khan$annotation$Symbol

#plot(k.bga, genelabels=gene.symbs)    need to define gene;symbs
